%% Copy-Move-------------------------------------------------------------------
%%%% Key-point-based
\bibitem{ref:keypoint-1}
X. Pan and S. Lyu,
\textit{``Region duplication detection using image feature matching"},
IEEE Transactions on Information Forensics and Security,
vol. 5, no.4, ISSN: 1556-6013, pp. 857-867, 2010.
	
\bibitem{ref:keypoint-2}
I. Amerini, L. Ballan, R. Caldelli, A. Del Bimbo and G.Serra,
\textit{``A sift-based forensic method for copy–move attack detection and transformation recovery"},
IEEE Transactions on Information Forensics and Security,
vol. 6, no. 3, ISSN: 1556-6013, pp. 1099-1110, 2011.

\bibitem{ref:keypoint-3}
P. Kakar, N. Sudha,
\textit{``Exposing postprocessed copy-paste forgeries through transform-invariant feature"},
IEEE Transactions on Information Forensics and Security,
vol. 7, no. 3, ISSN: 1556-6013, pp. 1018-1028, June 2012.

%%%% Block-based
\bibitem{ref:block-1}
S.-J. Ryu, M.-J. Lee and H.-K. Lee,
\textit{``Detection of copy-rotate-move forgery using Zernike moments"},
Information Hiding Conference, Lecture Notes in Computer Science, vol. 6387, Springer,
Heidelberg-Berlin, 2010, ISBN: 978-3-642-16434-7.

\bibitem{ref:block-2}
H.-J. Lin, C.-W. Wang and Y.-T. Kao,
\textit{``Fast copy-move forgery detection"},
WSEAS Transactions on Signal Processing,
vol. 5, no. 5, ISSN: 0031-3203, pp. 188-1975, 2009.

\bibitem{ref:block-3}
V. Christlein, C. Riess, J. Jordan and E. Angelopoulou,
\textit{``An evaluation of popular copy-move forgery detection approaches"},
IEEE Transactions on Information Forensics and Security,
vol. 7, no. 6, ISSN: 1556-6013, pp. 1841-1854, 2012.

\bibitem{ref:block-4}
T. L.-Tien, T. H.-Kha, L. P.-C.-Hoan, A. T.-Hong, N. Dey, M. Luong,
\textit{``Combined Zernike Moment and Multiscale Analysis for Tamper Detection in Digital Images"},
Informatica (An International Journal of Computing and Informatics),
vol.41, no.1, ISSN: 0350-5596, March 2017.


%% JPEG format-----------------------------------------------------------------
\bibitem{ref:jpeg-dct-1}
Z. Lin, J. He, X. Tang, K. Tang,
\textit{``Fast, automatic and fine-grained tampered JPEG image detection via DCT coefficient analysis"},
Pattern Recognition, vol. 42, no. 11, ISSN: 0031-3203, pp. 2492-2501, January 2009.

\bibitem{ref:jpeg-dct-2}
W. Wang, J. Dong, T. Tan,
\textit{``Exploring DCT coefficient quantization effects for local tampering detection"},
IEEE Transactions on Information Forensics and Security,
vol. 9, no. 10, ISSN: 1556-6013, pp. 1653-1666, October 2014.

\bibitem{ref:jpeg-periodicity}
L. Chen, T. Hsu,
\textit{``Detecting recompression of JPEG images via periodicity analysis of compression artifacts for tampering detection"},
IEEE Transactions on Information Forensics and Security,
vol. 6, no. 2, ISSN: 1556-6013, pp. 396-406, June 2011.

\bibitem{ref:jpeg-improved}
L. Thing, Y. Chen, C. Cheh,
\textit{``An improved double compression detection method for JPEG image forensics"},
In IEEE International Symposium on Multimedia,
pages 290-297, December 2012, ISBN: 978-1-4673-4370-1.

\bibitem{ref:jpeg-ghosts}
F. Zach, C. Riess, and E. Angelopoulou,
\textit{``Automated image forgery detection through classification of JPEG ghosts"},
Pattern Recognition, 7476, pp. 185-194, January 2012.

\bibitem{ref:jpeg-block-grained}
T. Bianchi, A. Piva,
\textit{``Image forgery localization via block-grained analysis of JPEG artifacts"},
IEEE Transactions on Information Forensics and Security,
vol. 7, no. 3, ISSN: 1556-6013, pp. 1003-1017, June 2012.

\bibitem{ref:jpeg-inpainting}
C. Chang, C. Yu, C. Chang,
\textit{``A forgery detection algorithm for exemplar-based inpainting images using multi-region relation"},
Journal Image and Vision Computing,
vol. 31, no. 1, ISSN: 0262-8856, pp. 57-71, MA-USA, 2013.


%% Deep Learning approach------------------------------------------------------
\bibitem{ref:cnn-median}
J. Chen, X. Kang, Y. Liu and Z. J. Wang,
\textit{``Median Filtering Forensics Based on Convolutional Neural Networks"},
IEEE Signal Processing Letters,
vol. 22, no. 11, ISSN: 1070-9908, pp. 1849-1853, November 2015.

\bibitem{ref:cnn-universal}
B. Bayar, M. C. Stamm,
\textit{``A Deep Learning Approach to Universal Image Manipulation Detection Using a New Convolutional Layer"},
Proceedings of the 4th ACM Workshop on Information Hiding and Multimedia Security,
pp. 5-10, New York-USA, 2016, ISBN: 978-1-4503-4290-2.

\bibitem{ref:cnn-srm}
Rao Yuan, Ni Jiangqun,
\textit{``A deep learning approach to detection of splicing and copy-move forgeries in images"},
IEEE International Workshop on Information Forensics and Security (WIFS),
Abu Dhabi-United Arab Emirates, 2016, ISBN: 978-1-5090-1139-1.

\bibitem{ref:cnn-alex}
J.Ouyang, Y.Liu, M.Liao,
\textit{``Copy-Move Forgery Detection Based on Deep Learning"},
10th International Congress on Image and Signal Processing, BioMedical Engineering and Informatics,
Shanghai-China, 2017, ISBN: 978-1-5386-1938-4.

\bibitem{ref:dae}
Y. Zhang, J. Goh, L. Win, V. Thing,
\textit{``Image Region Forgery Detection: A Deep Learning Approach"},
Proceedings of the Singapore Cyber-Security Conference, Singapore, 2016, ISBN: 978-1-61499-616-3.


%% Database--------------------------------------------------------------------
\bibitem{ref:casia}
J. Dong and W. Wang,
\textit{``Casia tampering detection dataset"}, 2011.


%% Machine Learning------------------------------------------------------------
\bibitem{ref:alex-net}
A. Krizhevsky, I. Sutskever, G. Hinton,
\textit{``Imagenet classification with deep convolutional neural networks"},
NIPS'12 Proceedings of the 25th International Conference on Neural Information Processing Systems,
vol. 1, pp. 1097-1105, Nevada-USA, 2012, DOI: 10.1145/3065386.

\bibitem{ref:dropout}
N. Srivastava, 	G. Hinton, A. Krizhevsky, I. Sutskever, R. Salakhutdinov,
\textit{``Dropout: a simple way to prevent neural networks from overfitting"},
The Journal of Machine Learning Research,
vol. 15, no. 1, ISSN 1533-7928, pp. 1929-1958, January 2014.

\bibitem{ref:xavier}
Xavier Glorot, Yoshua Bengio,
\textit{``Understanding the difficulty of training deep feedforward neural networks"},
Proceedings of the 13rd International Conference on Artificial Intelligence and Statistics,
PMLR 9, pp. 249-256, Sardinia-Italy, \url{http://proceedings.mlr.press/v9/glorot10a/glorot10a.pdf}, 2010.

\bibitem{ref:relu}
V. Nair, E. Hinton,
\textit{``Rectified Linear Units Improve Restricted Boltzmann Machines"},
Proceedings of the 27th International Conference on Machine Learning,
pp. 807-814, Haifa-Israel, 2010, ISBN: 978-1-60558-907-7.

\bibitem{ref:leaky-relu-1}
B. Xu, N. Wang, T. Chen, M. Li,
\textit{``Empirical Evaluation of Rectified Activations in Convolutional Network"},
\url{https://arxiv.org/abs/1505.00853v2}, 2015.

\bibitem{ref:leaky-relu-2}
K. He, X. Zhang, S. Ren, J. Sun
\textit{``Delving Deep into Rectifiers: Surpassing Human-Level Performance on ImageNet Classification"},
\url{https://arxiv.org/abs/1502.01852v1}, 2015.

\bibitem{ref:adam}
P. Kingma, J. Ba,
\textit{``Adam: A Method for Stochastic Optimization"},
3rd International Conference for Learning Representations, San Diego-USA,
\url{https://arxiv.org/abs/1412.6980}, 2015.


%% Comparison------------------------------------------------------------------
\bibitem{ref:goh}
J. Goh and V. L. L. Thing,
\textit{``A hybrid evolutionary algorithm for feature and ensemble selection in image tampering detection"},
International Journal of Electronic Security and Digital Forensics,
vol. 7, no. 1, ISSN: 1751-911X, pp. 76-104, March 2015.

\bibitem{ref:he}
Z. He, W. Lu, W. Sun, J. Huang,
\textit{``Digital image splicing detection based on Markov features in DCT and DWT domain"},
Pattern Recognition, vol. 45, no. 12, ISSN: 0031-3203, pp. 4292-4299, 2012.


%% Appendix--------------------------------------------------------------------
\bibitem{ref:prove-wavelet}
A. Cohen, T. Tiplica, and A. Kobi,
\textit{``Design of experiments and statistical process control using wavelets analysis"},
Control Engineering Practice,
vol. 49, ISSN: 0967-0661, pp. 129-183, April 2016.

